---
title: "HW#3"
author: "Eden Kim"
output:
  pdf_document: default
---
# 1. Problem 4.7
ANOVA Table of problem 3.8

source | DF | SS    | MS   | F   | P     |
-------|----|-------|------|-----|-------|
Factor | 4  |987.71 |246.93|33.09|<0.0001|
Error  | 25 |186.53 |7.46
Total  | 29 |1174.24| 

New ANOVA Table  

source | DF | SS    | MS   | F   | P     |
-------|----|-------|------|-----|-------|
Factor | 5  |1234.65|246.93|33.10|<0.0001|
Block  | 5  |80.00  |16.00 |
Error  | 25 |186.53 |7.46  |
Total  | 29 |1174.24|

F value for both table does not change significantly (the change is less than 0.01). Since the p value is less than 0.0001, we reject the null hypothesis. 


# 2. Problem 4.19
## (a) Is there any evidence that stirring rate affects grain size?
```{r}
rate <- factor(c(rep(5, 4),rep(10,4),rep(15,4),rep(20,4)))
grainsize <- c(8,4,5,6,14,5,6,9,14,6,9,2,17,9,3,6)
furnance <- factor(rep(seq(1,4,1),4))
m1 <- aov(grainsize~rate+furnance)
summary(m1)
```
We get that f value is 0.853 and the p value is 0.4995 > 0.05 which shows that we failed to reject the null. From this we can conclude that this data is not enough to show that there is any evidence that stirring rate affects grain size. 


## (b) Graph the residuals from this experiment on a normal probability plot. Interpret this plot.
```{r}
qqnorm(m1$residuals)
qqline(m1$residuals)
```
This plot looks like they are somewhat normally distributed. Many of the data are slightly below the normal line, indicating some errors are accounted for this data. 


## (c) Plot the residuals versus furnace and stirring rate. Does this plot convey any useful information?
```{r}
plot(m1$fitted.values,m1$residuals)
```
This plot looks like the points are clustered towards the left side and there is no points in the middle. It looks like that the points on the right side of the plot is outliers. This shows that the residuals and furnances + stiring rate are not quite random and dependent of each other. The variance of the residuals is not constant over furnances and stiring rate.


## (d) What should the process engineers recommend concerning the choice of stirring rate and furnace for this particular grain refiner if small grain size is desirable?
There is no effect due to the stirring rate and furnace.



# 3. Problem 4.27
```{r}
# Latin Square
# Creating data variables from the table
batch <- factor(rep(seq(1,5,1),5))
day <- factor(c(rep(1,5),rep(2,5),rep(3,5),rep(4,5),rep(5,5)))
ingredient <- factor(c("A","C","B","D","E",
              "B","E","A","C","D",
              "D","A","C","E","B",
              "C","D","E","B","A",
              "E","B","D","A","C"))
time <- c(8,11,4,6,4,7,2,9,8,2,1,7,10,6,3,7,3,1,6,8,3,8,5,10,8)
# data frame
data.frame(batch,day,ingredient,time)

# Boxplots for different treatments and nuisance factors
boxplot(time~batch, xlab = "batch")
boxplot(time~day, xlab = "day")
boxplot(time~ingredient, xlab = "ingredient")

# ANOVA table
m2 <- aov(time~batch+day+ingredient)
summary(m2)

# check for model adequacy
qqnorm(m2$residuals)
qqline(m2$residuals)
plot(m2$fitted.values,m2$residuals)

# TukeyHSD for multiple comparison
TukeyHSD(m2)$ingredient
```
The f value is 11.309 and p value = 0.000488 < 0.05 so we reject the null hypothesis. We conclude that there is difference among ingredients. By looking at the qq plot, we see that the graph is close to normal and satisfies the normality. The variance is also pretty well spread throughout the graph. From the Tukey comparison table, the combination of the ingredients (D,A), (E,A), (E,C), and (D,C) have p value less than 0.05, so those ingredient combinations are statistically significant in the reaction of the chemical process.



# 4. Problem 4.40
```{r}
# Greek-Latin square
# Creating data variables from the table
batch2 <- factor(rep(seq(1,5,1),5))
acid <- factor(c(rep(1,5),rep(2,5),rep(3,5),rep(4,5),rep(5,5)))
latin <- factor(c("A","B","C","D","E",
          "B","C","D","E","A",
          "C","D","E","A","B",
          "D","E","A","B","C",
          "E","A","B","C","D"))
greek <- factor(c("a","c","e","b","d",
              "b","d","a","c","e",
              "c","e","b","d","a",
              "d","a","c","e","b",
              "e","b","d","a","c"))
yield <- c(26,18,20,15,10,16,21,12,15,24,19,18,16,22,17,16,11,25,14,17,13,21,13,17,14)
# data frame
data.frame(batch2,acid,latin,greek,yield)

# Latin square design
latinmodel <- aov(yield~latin+batch2+acid)
summary(latinmodel)

# Graeco-Latin square design
greekmodel <- aov(yield~latin+batch2+acid+greek)
summary(greekmodel)
```
From the two ANOVA table, we can observed that adding a catalyst concentration to the model increased the MSE of the model from 4.9 to 5.85 and reduced the degrees of freedom from 12 to 8. Thus, our estimate of error has fewer dgrees of freedom, and the test may be less sensitive. Since the analysis is to test the effect of different standing times to the yield of a chemical process, we see the F value 17.490 as the test statistic. Since the corresponding p-value = 6.03e-05 is less than 0.05, we reject the null hypothesis. 


# 5. Problem 4.47
```{r}
# BIBD
# creating data variables from the data table
concentration <- factor(c(2,4,8,4,6,10,6,8,12,8,10,14,2,10,12,4,12,14,2,6,14))
days <- factor(c(rep(1,3),rep(2,3),rep(3,3),rep(4,3),rep(5,3),rep(6,3),rep(7,3)))
strength <- c(114,126,141,120,137,145,117,129,120,149,150,136,120,143,118,119,123,130,117,134,127)
# data frame
data.frame(concentration,days,strength)

# BIBD model
bibdmodel <- aov(strength~concentration+days)
summary(bibdmodel)

TukeyHSD(bibdmodel)$concentration
```
We find that the f value is 16.11 and the p value is 0.000451 < 0.05, so we reject the null hypothesis and conclude that there is difference among the hardwood concentration. From the Tukey test, the pairs (6,2), (8,2), (10,2), (8,4),(10,4),(10,6),(12,8),(12,10), and (14,10) are statistically significant. It appears that the concentration 10% significatly effects on the strength of the paper by all other different concentrations. 
