---
title: "LAB"
output: html_document
---
1. 
(a) 400 observations
(b) Gender, APOL, RS174548, RS4775401, HTN, CHD
```{r}
library(readr)
cholesterol <- read_csv("Downloads/stats20/cholesterol.csv")
dim(cholesterol)
summary(cholesterol)
```
2.
```{r}
mean(cholesterol$TG)
median(cholesterol$TG)
sd(cholesterol$TG)
IQR(cholesterol$TG)
```
3. Based on the qqplot, the distribution of Serum triglycerides is approximately normal, since the line has a positive slope.
```{r}
library(MASS)
library(dplyr)
TGgraph <- hist(cholesterol$TG) %>% rnorm()
qqnorm(TGgraph)
qqline(TGgraph)
```
4. 
```{r}
boxplot(cholesterol$TG ~ cholesterol$GENDER, horizontal = TRUE, 
        col = c("blue", "green"), ylab = "Gender", xlab = "Serum triglycerides",
        main = "boxplot of gender and serum triglycerides")
```
5. 
```{r}
for(i in 1:length(cholesterol)){
  cholesterol$BMI_CAT[i] <- ifelse(cholesterol$BMI[i] >= 18 & cholesterol$BMI[i] < 25, "normal", 
                            ifelse(cholesterol$BMI[i] >= 25 & cholesterol$BMI[i] < 30, "overweight",
                            ifelse(cholesterol$BMI[i] > 30, "obese")))
}
```
6. 45.25% of the patients are overweight or obese.
```{r}
for(i in 1:length(cholesterol)){
  cholesterol$BMI_BIN[i] <- ifelse(cholesterol$BMI[i] >= 25, 1, 
                            ifelse(cholesterol$BMI_BIN[i] < 25, 0))
}

cholesterol$BMI_BIN %>% table() %>% prop.table()
```
7. 
```{r}
summary(cholesterol$TG[cholesterol$BMI_BIN==0])
summary(cholesterol$TG[cholesterol$BMI_BIN==1])
```
8. With BMI greater than 25 kg/m2, the average triglycerides tends to be higher than with BMI less than 25kg/m2. 
```{r}
boxplot(cholesterol$TG ~ cholesterol$BMI_BIN, horizontal = TRUE, col = c("yellow", "red"),
        xlab = "Triglycerides", ylab = "BMI")
```
9.
```{r}
t.test(cholesterol$TG ~ cholesterol$BMI_BIN)
```
10. The scatterplot shows that the serum triglycerides and BMI have a positive correlation, whereas the the boxplot easily demonstrates the average values of the two data set. 
```{r}
plot(cholesterol$TG ~ cholesterol$BMI)
```
11. The slope of serum trigylcerides and BMI is 15.44. That is, every 1 mg/dl increase in triglycerides gives 15.44kg/m2 increase in BMI

TG = 15.44(BMI) - 208.5
```{r}
reg <- lm(cholesterol$TG ~ cholesterol$BMI)
reg
```
12.
```{r}
plot(reg)
```